Test SUSIE for regions near genes (500kb flanking)

### 2020-06-23 analysis/simulation-susie-ukbchr22.Rmd
cbx7 locuszoom

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval=T)
```

@@

[Zoomlocus view for CBX7 region](https://users.rcc.uchicago.edu/~simingz/chr22_39026778-40048655.pdf)
```{r zoomlocus, out.width = "85%", include = F}
file.copy("/home/simingz/causalTWAS/simulations/simulation_ashtest_20200503/snp_200622_CBX7/chr22_39026778-40048655.pdf", "~/public_html/chr22_39026778-40048655.pdf")
```
